An Improved Method for Coupling Hydrodynamics with Astrophysical Reaction Networks

### 2022-05-10 simplified_sdc_intro/paper.tex
builds

\begin{figure}
\centering
\plotone{strang_subch2_cfl0.2_tols_slice}
\caption{\label{fig:subch_strang_cfl02} Temperature, mean molecular weight, and
energy generation rate for the Strang CFL = 0.2 run with normal tolerances ({\tt
strang_subch2\_cfl0.2}) at 0.1 s.}
\end{figure}

@@

\begin{figure}
\centering
\plotone{sdc_subch2_cfl0.2_tols_slice}
\caption{\label{fig:subch_sdc_cfl02} Temperature, mean molecular weight, and
energy generation rate for the simplified-SDC CFL = 0.2 run with normal tolerances ({\tt
sdc_subch2\_cfl0.2}) at 0.1 s.}
\end{figure}

>>>>

\begin{figure}
\centering
\plotone{strang_subch2_cfl0.2_tols_slice}
\caption{\label{fig:subch_strang_cfl02} Temperature, mean molecular weight, and
energy generation rate for the Strang CFL = 0.2 run with normal tolerances ({\tt
strang\_subch2\_cfl0.2}) at 0.1 s.}
\end{figure}

@@

\begin{figure}
\centering
\plotone{sdc_subch2_cfl0.2_tols_slice}
\caption{\label{fig:subch_sdc_cfl02} Temperature, mean molecular weight, and
energy generation rate for the simplified-SDC CFL = 0.2 run with normal tolerances ({\tt
sdc\_subch2\_cfl0.2}) at 0.1 s.}
\end{figure}
